Understanding the impact of electronically-delivered parenting advice

### 2019-02-08 paper/cogsci2019/cogsci2019.Rmd
cleaning up, merging analysis into writeup

Children spend a large portion of their waking time at play in their environment.
Playing with objects may allow them to discover hidden features, as well as to build a causal understanding of how the objects interact. 
Beyond learning object features, the laws of physics, and causal relationships (CITE), during play children practice motor skills that help them effectively navigate their world (Hirsh, 2008).
Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events (Hirsh, 2008).

## Guided Play Scaffolds Learning
Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings (Kaye, 1970). 
Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided (Vygotsky, 197X).
These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood" (Wood, 1970).
Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults" (Hirsh, 2008), 
have drawn researchers' interest. 
Weisberg showed that, with preschoolers, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg, Hirsh and Golinkoff, 2013).
Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills (Massey, 2013).

## Improving Parenting Practices and Language Use
- early interventions on parenting practices can help children's outcomes
Thus, including guided play in parenting practices early on is important and should help with children's later performances. Suskind did a parent-directed home-visiting intervention experiment in 2015, 
and found that parents in experimental group have greater knowledge of language development and this effect sustained after the experiment is done. 
However, more interactive outcomes, like parent word type and token numbers, child word types, conversational turn counts and child vocalization counts, 
increased during the home-visiting but did not sustain after four months of intervention [there are more detailed sustainibility differences of these measure. should I make it more clear?] (Suskind, 2015).
The fact that changes did not sustain could be due to the intervention itself, 
or could merely be that home-visiting is not sustainable enough for parents to easily and constantly get parenting advice.

## Effectiveness of Digital Delivery
-apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?

@@

@@

The data was analyzed according to our preregistration. [link]

@@

- calculate Type/Token Ratio (TTR)

Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
(otherwise a table with mean and SD of tokens, types, and TTR)
However, note that TTR is a measure that is correlated with the length of a text. ... 
According to Jarvis2010, MTLD is a better measure of lexical diversity.

@@

@@

```{r image, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=2, fig.height=2, set.cap.width=T, num.cols.cap=1, fig.cap = "One column image."}
img <- png::readPNG("figs/lab_logo_stanford.png")
grid::grid.raster(img)
```

## R Plots

You can use R chunks directly to plot graphs. And you can use latex floats in the
fig.pos chunk option to have more control over the location of your plot on the page. For more information on latex placement specifiers see **[here](https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions)**

```{r plot, fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=2, fig.height=2, fig.cap = "R plot" }
x <- 0:100
y <- 2 * (x + rnorm(length(x), sd = 3) + 3)

ggplot2::ggplot(data = data.frame(x, y), 
       aes(x = x, y = y)) + 
  geom_point() + 
  geom_smooth(method = "lm")
```

@@

```{r xtable, results="asis"}
n <- 100
x <- rnorm(n)
y <- 2*x + rnorm(n)
out <- lm(y ~ x)

tab1 <- xtable::xtable(summary(out)$coef, digits=c(0, 2, 2, 1, 2), 
                      caption = "This table prints across one column.")

print(tab1, type="latex", comment = F, table.placement = "H")
```

# Acknowledgements

Place acknowledgments (including funding information) in a section at
the end of the paper.

>>>>

Children spend a large portion of their waking time at play in their environment.
Playing with objects may allow them to discover hidden features, as well as to build a causal understanding of how the objects interact. 
Beyond learning object features, the laws of physics, and causal relationships [e.g., @Schulz2007], during play children practice motor skills that help them effectively navigate their world [@Singer2006].
Social play can help children learn about human relationships, both through imitation of adult behaviors and by experiencing and learning to process emotional events [@Singer2006].

## Guided Play Scaffolds Learning
Children's early play behaviors are often assisted by more skilled and knowledgeable play partners such as their caregivers and older siblings (Kaye, 1970). 
Under such expert guidance, children are encouraged and motivated to engage in more advanced play, undertaking explorations that push the boundaries of what they would be able to do unaided (Vygotsky, 197X).
These tutorial interactions have been shown to be a "a crucial feature of infancy and childhood" (Wood, 1970).
Thus, with the knowledge of both play and tutorial interactions, guided play, "where children actively engage in pleasurable and seemingly spontaneous activities under the direction of adults" (Hirsh-Pasek, 2008), 
have drawn researchers' interest. 
Weisberg showed that, with preschoolers, guided play scaffolds the environment while still allowing children to maintain a large degree of control, 
and it outperforms direct-instruction approaches in encouraging a variety of positive academic outcomes (Weisberg, Hirsh-Pasek and Golinkoff, 2013).
Massey specifically showed that guided play could facilitate children's vocabulary and comprehensive language development and subsequent literacy skills (Massey, 2013).

## Improving Parenting Practices and Language Use
(early interventions on parenting practices can help children's outcomes)
Thus, including guided play in parenting practices early on is important and should help with children's later performances. Suskind did a parent-directed home-visiting intervention experiment in 2015, 
and found that parents in experimental group have greater knowledge of language development and this effect sustained after the experiment is done. 
However, more interactive outcomes, like parent word type and token numbers, child word types, conversational turn counts and child vocalization counts, 
increased during the home-visiting but did not sustain after four months of intervention (there are more detailed sustainibility differences of these measure. should I make it more clear?) [@Suskind2015].
The fact that changes did not sustain could be due to the intervention itself, 
or could merely be that home-visiting is not sustainable enough for parents to easily and constantly get parenting advice.

## Effectiveness of Digital Delivery
(apps are an easy way to deliver curated, age-appropriate parenting advice — but can we measure an influence on parent's language? and do the interventions lead to children paying more attention?)

@@

```{r, echo=F}
e1path = "../../parenting_obs_e1/"
load(paste(e1path,"Exp1_cleaned_data.RData",sep=''))

```

@@

The data was analyzed according to our preregistration: [link](https://osf.io/2bpdf/).

@@

We first calculated Type/Token Ratio (TTR) for each transcript. ..

Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
(otherwise a table with mean and SD of tokens, types, and TTR)
However, note that TTR is a measure that is correlated with the length of a text. ... 
MTLD is a better measure of lexical diversity [@McCarthy2010].

@@

```{r, echo=F}
e2path = "../../parenting_obs_e2/"
#load(paste(e2path,"Exp2_cleaned_data.RData",sep=''))
e2d <- read.csv(paste(e2path,"MTLD_HDD.csv",sep=''), header=TRUE) 
```

@@

@@

### 2019-02-08 paper/cogsci2019/cogsci2019.tex
cleaning up, merging analysis into writeup

\textbf{Keywords:}
digital parenting advice; joint action; lexical diversity; guided play;
\end{abstract}

@@

\begin{itemize}
\tightlist
\item
  children learn through play -- physics, object features
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  guided play activities can scaffold children's language and reasoning
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  early interventions on parenting practices can help children's
  outcomes
\end{itemize}

@@

apps are an easy way to deliver curated, age-appropriate parenting
advice --- but can we measure an influence on parent's language? and do
the interventions lead to children paying more attention?

@@

The data was analyzed according to our preregistration. {[}link{]}

@@

\begin{itemize}
\tightlist
\item
  calculate Type/Token Ratio (TTR)
\end{itemize}

Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
(otherwise a table with mean and SD of tokens, types, and TTR) However,
note that TTR is a measure that is correlated with the length of a text.
\ldots{} According to Jarvis2010, MTLD is a better measure of lexical
diversity.

@@

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. Place the footnotes in 9 point type at the
bottom of the page on which they appear. Precede the footnote with a
horizontal rule.\footnote{Sample of the second footnote.} You can also
use markdown formatting to include footnotes using this
syntax.\footnote{Sample of a markdown footnote.}

@@

{\centering \includegraphics{figs/image-1}

\caption[One column image]{One column image.}\label{fig:image}
\end{figure}
\end{CodeChunk}

\subsection{R Plots}\label{r-plots}

You can use R chunks directly to plot graphs. And you can use latex
floats in the fig.pos chunk option to have more control over the
location of your plot on the page. For more information on latex
placement specifiers see
\textbf{\href{https://en.wikibooks.org/wiki/LaTeX/Floats,_Figures_and_Captions}{here}}

{\centering \includegraphics{figs/plot-1}

\caption[R plot]{R plot}\label{fig:plot}
\end{figure}
\end{CodeChunk}

@@

\begin{table}[H]
\centering
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & -0.06 & 0.11 & -0.6 & 0.58 \\ 
  x & 2.19 & 0.10 & 21.0 & 0.00 \\ 
   \hline
\end{tabular}
\caption{This table prints across one column.} 
\end{table}

\section{Acknowledgements}\label{acknowledgements}

Place acknowledgments (including funding information) in a section at
the end of the paper.

@@

>>>>

\textbf{Keywords:}
digital parenting advice; joint attention; lexical diversity; guided
play;
\end{abstract}

@@

Children spend a large portion of their waking time at play in their
environment. Playing with objects may allow them to discover hidden
features, as well as to build a causal understanding of how the objects
interact. Beyond learning object features, the laws of physics, and
causal relationships (e.g., Schulz \& Bonawitz, 2007), during play
children practice motor skills that help them effectively navigate their
world (Singer, Golinkoff, \& Hirsh-Pasek, 2006). Social play can help
children learn about human relationships, both through imitation of
adult behaviors and by experiencing and learning to process emotional
events (Singer et al., 2006).

@@

Children's early play behaviors are often assisted by more skilled and
knowledgeable play partners such as their caregivers and older siblings
(Kaye, 1970). Under such expert guidance, children are encouraged and
motivated to engage in more advanced play, undertaking explorations that
push the boundaries of what they would be able to do unaided (Vygotsky,
197X). These tutorial interactions have been shown to be a ``a crucial
feature of infancy and childhood'' (Wood, 1970). Thus, with the
knowledge of both play and tutorial interactions, guided play, ``where
children actively engage in pleasurable and seemingly spontaneous
activities under the direction of adults'' (Hirsh-Pasek, 2008), have
drawn researchers' interest. Weisberg showed that, with preschoolers,
guided play scaffolds the environment while still allowing children to
maintain a large degree of control, and it outperforms
direct-instruction approaches in encouraging a variety of positive
academic outcomes (Weisberg, Hirsh-Pasek and Golinkoff, 2013). Massey
specifically showed that guided play could facilitate children's
vocabulary and comprehensive language development and subsequent
literacy skills (Massey, 2013).

@@

(early interventions on parenting practices can help children's
outcomes) Thus, including guided play in parenting practices early on is
important and should help with children's later performances. Suskind
did a parent-directed home-visiting intervention experiment in 2015, and
found that parents in experimental group have greater knowledge of
language development and this effect sustained after the experiment is
done. However, more interactive outcomes, like parent word type and
token numbers, child word types, conversational turn counts and child
vocalization counts, increased during the home-visiting but did not
sustain after four months of intervention (there are more detailed
sustainibility differences of these measure. should I make it more
clear?) (Susking et al., 2015). The fact that changes did not sustain
could be due to the intervention itself, or could merely be that
home-visiting is not sustainable enough for parents to easily and
constantly get parenting advice.

@@

(apps are an easy way to deliver curated, age-appropriate parenting
advice --- but can we measure an influence on parent's language? and do
the interventions lead to children paying more attention?)

Digitally-delivered methods could address some logistic barriers to
face-to-face delivery methods. Bretenstein reviewed 11 studies on them
and showed good promise for the efficacy of interventions using
digitally-delivered methods. However, the parent and child outcomes
assessed in the review (e.g.infant positive behaviors, satisfaction,
emotional symptoms etc.) did not address the nature or quality of
parent-infant interactions at a detailed level, like if the
interventions lead to children paying more attention, or vocabulary
changes in parents' language usages. Thus, we want to conduct this
experiment to explore if and how digital scaffolding of activities
affect the social and linguistic characteristics of parent-child
ineractions.

@@

The data was analyzed according to our preregistration:
\href{https://osf.io/2bpdf/}{link}.

@@

We first calculated Type/Token Ratio (TTR) for each transcript. ..

Fig 1 - TTR, maybe also Total Tokens and Total Types (if subfigures fit)
(otherwise a table with mean and SD of tokens, types, and TTR) However,
note that TTR is a measure that is correlated with the length of a text.
\ldots{} MTLD is a better measure of lexical diversity (McCarthy \&
Jarvis, 2010).

@@

Indicate footnotes with a number\footnote{Sample of the first
footnote.} in the text. You can also use markdown formatting to include
footnotes using this syntax.\footnote{Sample of a markdown footnote.}

@@

@@

@@

\hypertarget{ref-McCarthy2010}{}
McCarthy, P. M., \& Jarvis, S. (2010). MTLD, vocd-d, and hd-d: A
validation study of sophisticated approaches to lexical diversity
assessment. \emph{Behavior Research Methods}, \emph{42}(2), 381--392.

\hypertarget{ref-Schulz2007}{}
Schulz, L., \& Bonawitz, E. (2007). Serious fun: Preschoolers engage in
more exploratory play when evidence is confounded. \emph{Developmental
Psychology}, \emph{43}(4), 1045--1050.

\hypertarget{ref-Singer2006}{}
Singer, D. G., Golinkoff, R. M., \& Hirsh-Pasek, K. (Eds.). (2006).
\emph{Play = learning: How play motivates and enhances children's
cognitive and social-emotional growth}. New York, NY: Oxford University
Press.

\hypertarget{ref-Suskind2015}{}
Susking, D. L., Leffel, K. R., Graf, E., Hernandez, M. W., Gunderson, E.
A., Sapolich, S. G., \ldots{} Levine, S. C. (2015). A parent-directed
language intervention for children of low socioeconomic status: A
randomized controlled pilot study. \emph{Journal of Child Language}.
\url{http://doi.org/10.1017/S0305000915000033}
